\myTitle

### 2023-11-29 body-text-of-paper.tex
Backslash-escape a rogue underscore

%%%
\begin{figure*}
\newcommand{\pigsimsqscap}{\footnotesize (A) The density of the estimated Q values from ADMIXTURE for
the simulated runs are
grouped across all population-combinations for each hybrid class and colored by the $K$ genetic cluster
(e.g., the Pop1 density plot for the $F_{1}BC_1$ plots the Pop1 genetic cluster for both
the Pop1-Pop2 and Pop1-Pop3 combinations). The density plots across the $K$
genetic clusters are mostly similar with the most variation among the genetic clusters evident in
the $F_1$ plot. (B) Plotting the density of the estimated Q values from ADMIXTURE for the $F_1$ hybrids,
separated by the population combinations, reveals the least variance in estimated Q values for
Pop1-Pop2 compared to Pop1-Pop3 and Pop2-Pop3. Note that these population combinations group the
reciprocal population combination in each plot (e.g., "Pop1_Pop2" has simulations
from both Pop1-Pop2 and Pop2-Pop1).}
\includegraphics[width=0.96\textwidth]{figures/simulation-density-multipanel.pdf}
\caption[\pigsimsqscap]{\pigsimsqscap}
\label{fig:pig-sim-qs}
\end{figure*}
%%%

>>>>

%%%
\begin{figure*}
\newcommand{\pigsimsqscap}{\footnotesize (A) The density of the estimated Q values from ADMIXTURE for
the simulated runs are
grouped across all population-combinations for each hybrid class and colored by the $K$ genetic cluster
(e.g., the Pop1 density plot for the $F_{1}BC_1$ plots the Pop1 genetic cluster for both
the Pop1-Pop2 and Pop1-Pop3 combinations). The density plots across the $K$
genetic clusters are mostly similar with the most variation among the genetic clusters evident in
the $F_1$ plot. (B) Plotting the density of the estimated Q values from ADMIXTURE for the $F_1$ hybrids,
separated by the population combinations, reveals the least variance in estimated Q values for
Pop1-Pop2 compared to Pop1-Pop3 and Pop2-Pop3. Note that these population combinations group the
reciprocal population combination in each plot (e.g., "Pop1\_Pop2" has simulations
from both Pop1-Pop2 and Pop2-Pop1).}
\includegraphics[width=0.96\textwidth]{figures/simulation-density-multipanel.pdf}
\caption[\pigsimsqscap]{\pigsimsqscap}
\label{fig:pig-sim-qs}
\end{figure*}
%%%
